### 2011-07-29 docs/Capitulos/listaCompras.tex
Se modifica documentación, esta versión del pdf se entrega el 29/7/2011 como pre-entrega de la documentación, aún sin finalizar.

\section{SBC}
\begin{table}[htbp]
\begin{center}
\begin{tabular}{|l|l|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
SBC & Beagleboard  RevC4 & 1 & 125 & 125 \\ \hline
Memoria SD & 4GB SDHC Class 6 SD Card & 1 & 15 & 15 \\ \hline
Cable serial DB9 nulo & DB9F Null Modem (RS-232) (6-ft) & 1 & 4 & 4 \\ \hline
Cable conversor usb–serial & USB to DB9M RS-232 (PL-2302) & 1 & 10 & 10 \\ \hline
Cable USB & USB Mini-A to USB A Female, OTG & 1 & 9 & 9 \\ \hline
Cable USB & USB Mini-B Male to USB A Male & 1 & 5 & 5 \\ \hline
Fuente  & 5VDC/2,5A & 1 & 10 & 10 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 178 \\ \hline
\end{tabular}
\end{center}
\caption{}
\label{}
\end{table}

\newpage
\section{PCBs}

\begin{table}[htbp]
\begin{center}
\begin{tabular}{|l|l|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
VLT & Interfaz entre SBC y SCUI & 1 & 28 & 28 \\ \hline
SCUI & Interfaz de usuario y lector de tarjetas ISO7816 & 1 & 53 & 53 \\ \hline
RWD RFID & Lector/Escritor de tarjetas RFID ISO14443 & 1 & 64 & 64 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 145 \\ \hline
\end{tabular}
\end{center}
\caption{PCBs}
\label{}
\end{table}

\section{VLT}
\begin{table}[tbp]
\begin{tabular}{|l|p{3cm}|p{2cm}|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
C1 & Polarized Capacitor (Tantal) & 6032[2312] & 10uF, 25V & 1 & 1,09 & 1,09 \\ \hline
C2 & Polarized Capacitor (Tantal) & 6032[2312] & 100uF, 6V3 & 1 & 1,16 & 1,16 \\ \hline
U4 & Regulador LM1117-3.3 & SOT-223 & 3.3V, 800mA & 1 & 1,1 & 1,1 \\ \hline
U1, U2, U3 & Voltage Level Translator & TSSOP20 & - & 3 & 2,24 & 6,72 \\ \hline
P1 & RECEPTACLE, 28WAY, 2ROW & SMD  Pitch 2,54 & 28 pines & 1 & 4,19 & 4,19 \\ \hline
P2 & RECEPTACLE, 40WAY, 2ROW & SMD  Pitch 2,54 & 40 pines & 1 & 4,36 & 4,36 \\ \hline
P1b & HEADER, 28WAY, 2ROW & T H Pitch 2,54 & 28 pines & 1 & 2 & 2 \\ \hline
P2b & HEADER, 40WAY, 2ROW & T H Pitch 2,54 & 40 pines & 1 & 1,94 & 1,94 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 22,56 \\ \hline
\end{tabular}
\caption{VLT}
\label{}
\end{table}

\newpage

\section{SCUI}
\begin{table}[htbp]
\begin{tabular}{|l|p{2.5cm}|p{2cm}|p{2cm}|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
R9 & Resistor 100W 1/4W 1\%  & 3216[1206] & 100W 1/4W  1\% & 1 & 0,07 & 0,07 \\ \hline
R10, R13 & Resistor 100KW 1/4W 5\%  & 3216[1206] & 100KW 1/4W   5\% & 2 & 0,09 & 0,18 \\ \hline
R11, R12, R14 & Resistor 10KW 1/4W 5\%  & 3216[1206] & 10KW 1/4W   5\% & 3 & 0,08 & 0,24 \\ \hline
Q2 & TRANSISTOR, NPN, 300MHZ & SOT23 & MMBT3904 & 1 & 0,125 & 0,125 \\ \hline
Q3 & TRANSISTOR, PNP, 250MHZ & SOT23 & MMBT3906 & 1 & 0,18 & 0,18 \\ \hline
J2 & SIM socket (6 contacts) & SMD & - & 1 & 1,25 & 1,25 \\ \hline
JP3, JP4 & HEADER, 1ROW, 3WAY & T H Pitch 2,54 & 3 pines & 2 & 0,11 & 0,22 \\ \hline
X1 & Oscillator 3.579545MHz & SMD & 3.579545 Mhz & 1 & 5,25 & 5,25 \\ \hline
ESD1 & Anti ESD & SOT323 & 6V / 150W & 1 & 0,45 & 0,45 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 7,965 \\ \hline
\end{tabular}
\caption{SC}
\label{}
\end{table}

%LCD
\begin{table}[htbp]
\begin{tabular}{|l|p{3cm}|p{2cm}|p{2cm}|c|c|c|}%|l|l|c|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
R1 & Resistor 4K7    1/10W     1\% & 1608[0603] & 4,7KW  1/10W   1\% & 1 & 0,05 & 0,05 \\ \hline
R2, R8 & Resistor 3R3    1/10W     1\% & 1608[0603] & 3,3W    1/10W   1\% & 2 & 0,09 & 0,18 \\ \hline
R3, R4, R5 & Resistor 680R  1/10W     1\% & 1609[0603] & 680W   1/10W   1\% & 3 & 0,05 & 0,15 \\ \hline
R6, R7 & Resistor 10K    1/10W     1\% & 1608[0603] & 10KW  1/10W   1\% & 2 & 0,05 & 0,1 \\ \hline
RV1 & Preset 15K        1/10W  25\% & SMD & 15KW   1/10W  25\% & 1 & 0,71 & 0,71 \\ \hline
Q1 & TRANSISTOR, NPN, 300MHZ & SOT23 & MMBT3904 & 1 & 0,125 & 0,125 \\ \hline
S1 & LCD MODULE 16X2 CHARACTER & Pitch 2,54 & - & 1 & 10,85 & 10,85 \\ \hline
CONN1 & HEADER FEMALE 16POS.1" TIN & Through Hole & 16 pines & 1 & 1,25 & 1,25 \\ \hline
CONN2 & HEADER, 1ROW, 16WAY & T H Pitch 2,54 & 16 pines & 1 & 0,155 & 0,155 \\ \hline
LED1 & Led green 5mm & Through Hole & 1,9V,  2mA & 1 & 0,11 & 0,11 \\ \hline
LED2 & Led red 5mm & Through Hole & 1,9V,  2mA & 1 & 0,1 & 0,1 \\ \hline
LED3 & Led yellow 5mm & Through Hole & 2,4V,  2mA & 1 & 0,13 & 0,13 \\ \hline
BUZZ1 & Buzzer & Through Hole & 3~20Vdc, 3~16mA & 1 & 5,31 & 5,31 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 19,17 \\ \hline
\end{tabular}
\caption{LCD}
\label{}
\end{table}

\newpage
\section{Lector-Escritor RFID}
\begin{table}[htbp]
\begin{tabular}{|l|p{2cm}|p{2cm}|p{2.5cm}|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
C1, C2 & Capacitor & 1608[0603] & 10pF,   Ceramic NPO, 2\% & 2 & 0,135 & 0,27 \\ \hline
C3, C4 & Capacitor & 1609[0603] & 100pF, Ceramic NPO, 2\% & 2 & 0,194 & 0,388 \\ \hline
C5, C6, C7, C8 & Capacitor & 1608[0603] &  NC & 4 & - & 0 \\ \hline
R1,  R2 & Resistor & 1608[0603] & 0W,  1/10W,  1\% & 2 & 0,015 & 0,03 \\ \hline
 &  &  &  &  &  & 0,688 \\ \hline
\end{tabular}
\caption{Inductor + Adaptaci\'on}
\label{}
\end{table}

>>>>

\section{SBC}
\begin{longtable}{|l|l|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
SBC & Beagleboard  RevC4 & 1 & 125 & 125 \\ \hline
Memoria SD & 4GB SDHC Class 6 SD Card & 1 & 15 & 15 \\ \hline
Cable serial DB9 nulo & DB9F Null Modem (RS-232) (6-ft) & 1 & 4 & 4 \\ \hline
Cable conversor usb–serial & USB to DB9M RS-232 (PL-2302) & 1 & 10 & 10 \\ \hline
Cable USB & USB Mini-A to USB A Female, OTG & 1 & 9 & 9 \\ \hline
Cable USB & USB Mini-B Male to USB A Male & 1 & 5 & 5 \\ \hline
Fuente  & 5VDC/2,5A & 1 & 10 & 10 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 178 \\ \hline
\caption{SBC}
\label{}
\end{longtable}

\newpage
\section{PCBs}
\begin{longtable}{|l|l|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
VLT & Interfaz entre SBC y SCUI & 1 & 28 & 28 \\ \hline
SCUI & Interfaz de usuario y lector de tarjetas ISO7816 & 1 & 53 & 53 \\ \hline
RWD RFID & Lector/Escritor de tarjetas RFID ISO14443 & 1 & 64 & 64 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 145 \\ \hline
\caption{PCBs}
\label{}
\end{longtable}

\section{VLT}
\begin{longtable}{|l|p{3cm}|p{2cm}|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
C1 & Polarized Capacitor (Tantal) & 6032[2312] & 10uF, 25V & 1 & 1,09 & 1,09 \\ \hline
C2 & Polarized Capacitor (Tantal) & 6032[2312] & 100uF, 6V3 & 1 & 1,16 & 1,16 \\ \hline
U4 & Regulador LM1117-3.3 & SOT-223 & 3.3V, 800mA & 1 & 1,1 & 1,1 \\ \hline
U1, U2, U3 & Voltage Level Translator & TSSOP20 & - & 3 & 2,24 & 6,72 \\ \hline
P1 & RECEPTACLE, 28WAY, 2ROW & SMD  Pitch 2,54 & 28 pines & 1 & 4,19 & 4,19 \\ \hline
P2 & RECEPTACLE, 40WAY, 2ROW & SMD  Pitch 2,54 & 40 pines & 1 & 4,36 & 4,36 \\ \hline
P1b & HEADER, 28WAY, 2ROW & T H Pitch 2,54 & 28 pines & 1 & 2 & 2 \\ \hline
P2b & HEADER, 40WAY, 2ROW & T H Pitch 2,54 & 40 pines & 1 & 1,94 & 1,94 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 22,56 \\ \hline
\caption{VLT}
\label{}
\end{longtable}

\section{SCUI}
\begin{longtable}{|l|p{2.5cm}|p{2cm}|p{2cm}|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
R9 & Resistor 100W 1/4W 1\%  & 3216[1206] & 100W 1/4W  1\% & 1 & 0,07 & 0,07 \\ \hline
R10, R13 & Resistor 100KW 1/4W 5\%  & 3216[1206] & 100KW 1/4W   5\% & 2 & 0,09 & 0,18 \\ \hline
R11, R12, R14 & Resistor 10KW 1/4W 5\%  & 3216[1206] & 10KW 1/4W   5\% & 3 & 0,08 & 0,24 \\ \hline
Q2 & TRANSISTOR, NPN, 300MHZ & SOT23 & MMBT3904 & 1 & 0,125 & 0,125 \\ \hline
Q3 & TRANSISTOR, PNP, 250MHZ & SOT23 & MMBT3906 & 1 & 0,18 & 0,18 \\ \hline
J2 & SIM socket (6 contacts) & SMD & - & 1 & 1,25 & 1,25 \\ \hline
JP3, JP4 & HEADER, 1ROW, 3WAY & T H Pitch 2,54 & 3 pines & 2 & 0,11 & 0,22 \\ \hline
X1 & Oscillator 3.579545MHz & SMD & 3.579545 Mhz & 1 & 5,25 & 5,25 \\ \hline
ESD1 & Anti ESD & SOT323 & 6V / 150W & 1 & 0,45 & 0,45 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 7,965 \\ \hline
\caption{SC}
\label{}
\end{longtable}

%LCD
\begin{longtable}{|l|p{3cm}|p{2cm}|p{2cm}|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
R1 & Resistor 4K7    1/10W     1\% & 1608[0603] & 4,7KW  1/10W   1\% & 1 & 0,05 & 0,05 \\ \hline
R2, R8 & Resistor 3R3    1/10W     1\% & 1608[0603] & 3,3W    1/10W   1\% & 2 & 0,09 & 0,18 \\ \hline
R3, R4, R5 & Resistor 680R  1/10W     1\% & 1609[0603] & 680W   1/10W   1\% & 3 & 0,05 & 0,15 \\ \hline
R6, R7 & Resistor 10K    1/10W     1\% & 1608[0603] & 10KW  1/10W   1\% & 2 & 0,05 & 0,1 \\ \hline
RV1 & Preset 15K        1/10W  25\% & SMD & 15KW   1/10W  25\% & 1 & 0,71 & 0,71 \\ \hline
Q1 & TRANSISTOR, NPN, 300MHZ & SOT23 & MMBT3904 & 1 & 0,125 & 0,125 \\ \hline
S1 & LCD MODULE 16X2 CHARACTER & Pitch 2,54 & - & 1 & 10,85 & 10,85 \\ \hline
CONN1 & HEADER FEMALE 16POS.1" TIN & Through Hole & 16 pines & 1 & 1,25 & 1,25 \\ \hline
CONN2 & HEADER, 1ROW, 16WAY & T H Pitch 2,54 & 16 pines & 1 & 0,155 & 0,155 \\ \hline
LED1 & Led green 5mm & Through Hole & 1,9V,  2mA & 1 & 0,11 & 0,11 \\ \hline
LED2 & Led red 5mm & Through Hole & 1,9V,  2mA & 1 & 0,1 & 0,1 \\ \hline
LED3 & Led yellow 5mm & Through Hole & 2,4V,  2mA & 1 & 0,13 & 0,13 \\ \hline
BUZZ1 & Buzzer & Through Hole & 3~20Vdc, 3~16mA & 1 & 5,31 & 5,31 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 19,17 \\ \hline
\caption{LCD}
\label{}
\end{longtable}

\section{Lector-Escritor RFID}
\begin{longtable}{|l|p{2cm}|p{2cm}|p{2.5cm}|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
C1, C2 & Capacitor & 1608[0603] & 10pF,   Ceramic NPO, 2\% & 2 & 0,135 & 0,27 \\ \hline
C3, C4 & Capacitor & 1609[0603] & 100pF, Ceramic NPO, 2\% & 2 & 0,194 & 0,388 \\ \hline
C5, C6, C7, C8 & Capacitor & 1608[0603] &  NC & 4 & - & 0 \\ \hline
R1,  R2 & Resistor & 1608[0603] & 0W,  1/10W,  1\% & 2 & 0,015 & 0,03 \\ \hline
 &  &  &  &  &  & 0,688 \\ \hline
\caption{Inductor + Adaptaci\'on}
\label{}
\end{longtable}

\begin{longtable}{|p{1cm}|p{2.5cm}|p{2cm}|p{2.5cm}|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Componente}} & \multicolumn{1}{c|}{\textbf{Descripción}} & \textbf{ Footprint} & \textbf{Valor} & \textbf{Cantidad} & \textbf{Precio x1} & \textbf{Total} \\ \hline
C10 & Capacitor & 1610[0603] & 10pF, Ceramic NPO, 2\% & 1 & 0,135 & 0,135 \\ \hline
C1, C2 & Capacitor & 1608[0603] & 15pF, Ceramic NPO, 5\% & 2 & 0,03 & 0,06 \\ \hline
C12, C13 & Capacitor & 1608[0603] & 56pF, Ceramic NPO, 2\% & 2 & 0,194 & 0,388 \\ \hline
C14, C15 & Capacitor & 1608[0603] & 68pF, Ceramic NPO, 1\% & 2 & 0,197 & 0,394 \\ \hline
C9 & Capacitor & 1609[0603] & 100pF, Ceramic NPO,  2\% & 1 & 0,194 & 0,194 \\ \hline
C16 & Capacitor & 1608[0603] & 1nF, Ceramic NPO, 10\% & 1 & 0,08 & 0,08 \\ \hline
C4, C5, C7, C8, C11, C17 & Capacitor & 1608[0603] & 100nF, Ceramic X7R, 10\% & 6 & 0,074 & 0,444 \\ \hline
C3, C6, C18 & Capacitor & 1608[0603] & 10uF, Ceramic X5R, 20\% & 3 & 0,195 & 0,585 \\ \hline
L1, L2, L3, L6 & Inductor & 2012[0805] & 22nH, 700mA, 5\% & 4 & 0,454 & 1,816 \\ \hline
L4, L5 & Inductor & 3225[1210] & 1uH, 400mA, 5\% & 2 & 0,29 & 0,58 \\ \hline
R3 & Resistor & 1608[0603] & 50W, 1/10W   1\% & 1 & 0,268 & 0,268 \\ \hline
R2 & Resistor & 1608[0603] & 820W, 1/10W   5\% & 1 & 0,027 & 0,027 \\ \hline
R1 & Resistor & 1608[0603] & 2,2KW, 1/5W   1\% & 1 & 0,08 & 0,08 \\ \hline
U1 & Reader ISO14443 & SO32 & CL RC632 & 1 & 14,22 & 14,22 \\ \hline
U2 & Crystal Oscillator, HC49 US SMD & 49USMXL & 13.56MHz, 10pF & 1 & 0,98 & 0,98 \\ \hline
U3 & Operational Amplifier (up to 7.5V) & SOT23-5 & OPA354 & 1 & 2,8 & 2,8 \\ \hline
CONN1, CONN2 & U.FL-R Connector & U.FL-R-SMT & - & 2 & 1,76 & 3,52 \\ \hline
J1 & HEADER, 10WAY, 2ROW & T H Pitch 2,54 & 10 pines & 1 & 0,389 & 0,389 \\ \hline
J1b & RECEPTACLE, 10WAY, 2ROW & SMD  Pitch 2,54 & 10 pines & 1 & 2,27 & 2,27 \\ \hline
 &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & 29,23 \\ \hline
\caption{CL RC632 + filtro EMC}
\label{}
\end{longtable}
